Tool-driven Revolutions in Archaeological Science

### 2018-09-10 analysis/paper/jcaa-paper.Rmd
yeah. right. let's simply "talk about"

As @Galison_1997 describes a shift in the practices of physicists, so does archaeological practice change in the digital age. What exactly this entails, is diverse and has been discussed more thoroughly by @Huvila_2018 who ventilate what questions on archaeological practices and knowledge work should be answered to avoid a technologically determisitic approach to computational archaeology.

>>>>

As @Galison_1997 describes a shift in the practices of physicists, so does archaeological practice change in the digital age. What exactly this entails, is diverse and has been discussed more thoroughly by @Huvila_2018 who talk about what questions on archaeological practices and knowledge work should be answered to avoid a technologically determisitic approach to computational archaeology.
